A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-03 paper/paper.Rmd
Move paper text into MDPI template format in /paper
* Uses MDPI template
* Updates tables
* Updates table contents with footnotes
* Uses proper cross-references for tables and figures
* Corrects order of figures in which they appear and are referenced
* Spelling corrections
* Grammar corrections
* et. al replaced with et al.

---
title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
author:
  - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
date: "Last Edit: `r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
      md_extensions: +styles
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: "../Mungbean.bib"
csl: "multidisciplinary-digital-publishing-institute.csl"
link-citations: yes
abstract: |
         **Abstract:** Insert abstract here.
---

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english, pander)

@@

::: {custom-style="Art_type"}
Type of Paper: Article
:::

::: {custom-style="keywords"}
**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
:::
<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->

## Introduction

@@

Powdery mildew is caused by two separate genera of fungi in Australia *Podosphaera xanthii* and an unnamed *Psuedoidium sp.* (Kiss and Kelly Personal Communication).
While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia which disseminate to new infection sites [@Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].

@@

The collection of experiments mentioned above and other unpublished trials present an excellent opportunity for a meta-analysis.
Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and produces a more accurate estimate of the true effect being measured.
Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
Typically meta-analyses consider the effect of a single treatment against a control group across multiple independent studies [@Madden2011]. 
However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
In-direct comparisons can be made between these two treatments if the both had direct comparisons with one or more treatments in common, assuming no significant bias in the studies which investigated each of the treatments which are subject to a indirect comparison [@Jansen2011].

@@

## Materials and Methods
**Trial criteria for inclusion and description :**
The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
Trial data were obtained in different formats with varying levels of information.
Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
Twenty six trials in total were collated.

@@

```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
# Add a star to the trials which were not in the final analysis
PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")

# Build table 
PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(
      year = unique(year),
      location = unique(location),
      planting_date = unique(planting_date),
      first_sign_disease = unique(first_sign_disease)
   ) %>%
   arrange(year) %>%
   mutate(Research_org = c(
      rep("Queensland DAF", times = 4),
      rep("Northern Growers Alliance", times = 4),
      rep("Queensland DAF", times = 4),
      rep("USQ", times = 5)
   )) %>%
   flextable()%>%
   set_caption("Table 1: Description of Experiments") %>%
   set_header_labels(trial_ref = "Unique Trial Reference",
                     year = "Year",
                     location = "Trial Location",
                     planting_date = "Planting Date",
                     first_sign_disease = "First sign of disease date",
                     Research_org = "Research organisation")%>%
   autofit(add_w = 0.5)%>%
   align(j = c(1,4,5), align = "center", part = "all")%>%
   fontsize(size = 9)%>%
   width(j = 1:4, 1)%>%
   width(j = 5, 1.1)%>%
   width(j = 6, 1.7)
```

@@

Similar to Paul *et. al.* [-@Paul2007], we fitted a multivariate random effects model
$Y_i \sim N(\mu,s_i^2 + \sigma^2)$
where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.

@@

An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2). 
However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward. 
The end of season mean plot severity, and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.  
<br>
```{r Table2_1to9Scale, echo=FALSE}
data.frame(
   Scale = 1:9,
   `Scale Description` = c(
      "No sign of powdery mildew",
      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
      "Colonies to top of the plant with > 75 % of plants affected",
      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
   )
) %>%
   flextable()%>%
   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
   set_header_labels(Scale.Description = "Scale Description")%>%
   autofit()%>%
   fontsize(size = 9)%>%
   align(j = c(1), align = "center", part = "all")%>%
   width(j = 2, 6.2)
```
<br>
The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments. A a Wald-type test was used to test the impact of the disease pressure factor.

@@

<br>

```{r Figure2_treatForest, echo = FALSE}
YieldContrasts
```

## Results

$control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively). 
However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

@@

```{r Figure1, echo=FALSE}
SeasonPlot
```

<br>
<br>

```{r table3_Contrasts, echo = FALSE}
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3[,2:5] <- round(T3[,2:5], 4)
T3 %>%
   mutate(contrasts = gsub("-","",contrasts))%>%
   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
   mutate(contrasts = gsub(" = 0","",contrasts))%>%
   flextable()%>%
   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
   autofit(add_w = 0.2)%>%
   align(j = c(2,3,4), align = "center", part = "all") %>%
   set_header_labels(contrasts = "Treatment contrasts",
                     estimates = "Estimate",
                     se = "Std Error",
                     z_val = "Z-Score",
                     pval = "P-Value",
                     VisP = " ")%>%
   fontsize(size = 9)%>%
   width(j = 5,0.7)%>%
   width(j = 6, .3)
```

## Discussion
The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017]. 
This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`). 
In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss by  `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
`r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg / ha in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure 1)
which again follows the advice given by Thompson et. al [@SueThompson2016].
This meta-analysis adds certainty to the advice which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
We show here Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.

This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease. 
Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing. 
Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs. 
However attention should be made to the label requirements when first planning a spray schedule.
Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.

It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure 1). 
While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
An example of this is if we inspect the six trials which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments. 
However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].

>>>>

---
title: A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean
author:
  - name: Paul Melloy
    affil: 1,*
    orcid: 0000-0003-4253-7167
  - name: Emerson Del Ponte
    affil: 2
    orcid: 0000-0003-4398-409X
  - name: Adam H. Sparks
    affil: 3
    orcid: 0000-0002-0061-8359
affiliation:
  - num: 1
    address: |
      University of Southern Queensland
      Centre for Crop Health
      Toowoomba, Queensland, 4350 Australia
    email: Paul.Melloy@usq.edu.au
  - num: 2
    address: |
      Universidade Federal de Viçosa
      Departamento de Fitopatologia
      Viçosa, 36570-000 Minas Gearais, Brazil
    email: delponte@ufv.br
  - num: 3
    address: |
      University of Southern Queensland
      Centre for Crop Health
      Toowoomba, Queensland, 4350 Australia
    email: Adam.Sparks@usq.edu.au
correspondence: |
  Paul.Melloy@usq.edu.au; Tel.: +61 7 4631 5527
journal: agronomy
type: article
status: submit
bibliography: ../Mungbean.bib
#appendix: appendix.tex
simplesummary: |
  A simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
   Please add: ``This research received no external funding'' or ``This research
   was funded by NAME OF FUNDER grant number XXX.'' and ``The APC was funded by
   XXX''. Check carefully that the details given are accurate and use the
   standard spelling of funding agency names at
   <https://search.crossref.org/funding>, any errors may affect your future
   funding.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, english, pander)

@@

@@

Powdery mildew is caused by two separate genera of fungi in Australia *Podosphaera xanthii* and an unnamed *Psuedoidium sp.* (Kiss and Kelly Personal Communication).
While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].

@@

The collection of experiments mentioned above and other unpublished trials present an excellent opportunity for a meta-analysis.
Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
Typically meta-analyses consider the effect of a single treatment against a control group across multiple independent studies [@Madden2011]. 
However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
Indirect comparisons can be made between these two treatments if the both had direct comparisons with one or more treatments in common, assuming no significant bias in the studies that investigated each of the treatments and which are subject to a indirect comparison [@Jansen2011].

@@

# Materials and Methods

## Trial criteria for inclusion and description

The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
Trial data were obtained in different formats with varying levels of information.
Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean.
Twenty six trials in total were collated.

@@

```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
# Add a star to the trials which were not in the final analysis
PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
  sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")

# Build table
PM_Mdat %>%
  filter(fungicide_ai == "tebuconazole" |
           fungicide_ai == "propiconazole") %>%
  group_by(trial_ref) %>%
  summarise(
    year = unique(year),
    location = unique(location),
    planting_date = unique(planting_date),
    first_sign_disease = unique(first_sign_disease)
  ) %>%
  arrange(year) %>%
  mutate(Research_org = c(
    rep("DAF$^{a}$", times = 4),
    rep("NGA$^{b}$", times = 4),
    rep("DAF$^{a}$", times = 4),
    rep("USQ$^{c}$", times = 5)
  )) %>%
  rename(
    `Unique Trial Reference` = trial_ref,
    Year = year,
    Location = location,
    `Planting Date` = planting_date,
    `Date First Sign` = first_sign_disease,
    `Research Organisation` = Research_org
  ) %>%
  kable(format = "latex",
        booktabs = TRUE,
        escape = FALSE,
        caption="Description of fungicide application experiments.") %>%
  kable_styling() %>%
  footnote(
    alphabet = c(
      "Queensland Department of Agriculture, Fisheries and Forestry",
      "Northern Growers Alliance",
      "University of Southern Queensland"
    )
  )
```

@@

Similar to Paul *et al..* [-@Paul2007], we fitted a multivariate random effects model
$Y_i \sim N(\mu,s_i^2 + \sigma^2)$
where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.

@@

An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2).
However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward.
The end of season mean plot severity, and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment.
Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available.
AUDPC was calculated using the `agricolae` package in R [@agricolae2020].
A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.

```{r Table2_1to9Scale, echo=FALSE}
data.frame(
  Scale = 1:9,
  `Scale Description` = c(
    "No sign of powdery mildew",
    "Small colonies in lower 1/3 of the canopy, up to 75 % of the plants affected",
    "Colonies in lower 1/2 of the canopy, > 75 % of the plants affected",
    "Colonies in lower 2/3 of the canopy, up to 75 % of the plants affected",
    "Colonies in lower 2/3 of the canopy, > 75 % of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100 % of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100 % of plants, with some plants with colonies in the top 1/3 of the canopy",
    "Colonies to top of the plant with > 75 % of the plants affected",
    "Colonies to top of the plant with > 100 % of the plants affected and heavy leaf drop"
  )
) %>%
kable(format = "latex",
      booktabs = TRUE,
      caption="Powdery mildew severity scoring scale.") %>%
  kable_styling()
```

The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
A a Wald-type test was used to test the impact of the disease pressure factor.

@@

```{r Figure1, echo = FALSE, caption = "Yield contrasts"}
YieldContrasts
```

# Results

$control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)). 
Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively). 
However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

@@

<!-- What is this `SeasonPlot`? I can't find any docs and no file named `SeasonPlot`. It should just be code here int the doc for easy editing. -->

```{r Figure2, echo=FALSE, caption="Season plot"}
SeasonPlot
```

```{r table3_Contrasts, echo = FALSE}
T3 <-
  read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3[, 2:5] <- round(T3[, 2:5], 4)
T3 %>%
  mutate(contrasts = gsub("-", "", contrasts)) %>%
  mutate(contrasts = gsub(" \\+", " -", contrasts)) %>%
  mutate(contrasts = gsub(" = 0", "", contrasts)) %>%
  rename(
    `Treatment contrasts` = contrasts,
    Estimate = estimates,
    `Standard Error` = se,
    `Z-score` = z_val,
    `P-value` = pval,
    ` ` = VisP
  ) %>%
  kable(format = "latex",
        booktabs = TRUE,
        caption = "Estimated grain yield contrasts between each spray schedule.") %>%
  kable_styling() %>%
  footnote(general = c("** - signficant at 0.005 level",
                       "* - signficant at 0.05 level"))
```

# Discussion
The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`). 
In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss by  `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
`r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg / ha in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2))
which again follows the advice given by Thompson et al. [@SueThompson2016].
This meta-analysis adds certainty to the advice, which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
We show here Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.

This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease. 
Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing. 
Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs. 
However attention should be made to the label requirements when first planning a spray schedule.
Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.

It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments. 
However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
